New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems\tnoteref{t1}

### 2020-08-17 paper/acknowledgments.tex
wip

We are very grateful for the editorial process conducted by this journal, every comment. The reviewers sent us very detailed and insightful comments and suggestions; without them, we could not have improved our work the way we did, reaching the quality it is now.

We would also like to express our gratitude to the funding institutions Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES), and Fundação de Amparo à Pesquisa do Estado de São Paulo (FAPESP)\footnote{Processes 2013/07375-0 and 2016/01860-1.} that made this research possible.

>>>>

We would like to thank the reviewers for their useful suggestions, that greatly improved this work.
We would also like to express our gratitude to the funding institutions Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES), and Fundação de Amparo à Pesquisa do Estado de São Paulo (FAPESP) (processes 2013/07375-0 and 2016/01860-1) that made this research possible.
